\begin{abstract}
Algorithmic trading systems have traditionally relied on virtual private servers (VPS) deployed in centralized data centers, incurring substantial network latency, recurring operational cost, and single points of failure. I present \textsc{HOOX}, an open-source, edge-native algorithmic trading framework that I implemented entirely on Cloudflare Workers. \textsc{HOOX} decomposes trading logic into ten specialized Workers that communicate via Cloudflare Service Bindings, achieving sub-millisecond inter-service call overhead and a median production latency of 22\,ms from webhook ingestion to centralized exchange (CEX) order acknowledgment on the direct execution path.

I distinguish two measurement regimes that prior summaries often conflate: (i)~\emph{synthetic fast-path probes}, which short-circuit before exchange submission and characterize internal mesh latency; and (ii)~\emph{production signal-to-ack}, which includes HMAC-signed REST placement and exchange response parsing. The system integrates four platform primitives uncommon in retail trading stacks: Durable Objects for strongly consistent duplicate suppression under concurrent webhook retries; Smart Placement for automatic proximity routing to exchange API origins; Cloudflare Queues with application-level exponential backoff for outage resilience; and a deterministic risk manager with optional multi-provider large language model (LLM) operational summaries.

Over a twelve-month production deployment (July 2025--July 2026) that I operated, the system processed signals with 99.97\% eventual success within five minutes during exchange maintenance windows and recorded zero duplicate fills attributable to idempotency failures. I document the architecture, security model, per-Worker implementation reference with annotated code listings, a multi-tier test methodology and failure taxonomy, and reproducible evaluation commands (\texttt{hoox perf fastpath}, k6 load tests). I discuss portability limits and applicability to other globally distributed, latency-sensitive control planes. The system and this paper are released under Creative Commons Attribution 4.0 (CC~BY~4.0).
\end{abstract}

\noindent\textbf{Keywords:} algorithmic trading, edge computing, serverless, Cloudflare Workers, low latency, idempotency, Durable Objects, service bindings, financial technology