\section{Introduction}
\label{sec:introduction}

Algorithmic trading requires executing strategies with minimal latency to capture fleeting market opportunities and manage risk effectively~\cite{hasbrouck2007empirical,hendershott2011does,hasbrouck2013lowlatency}. Traditional deployments place trading logic on virtual private servers (VPS) in fixed geographic regions. This architecture introduces substantial round-trip times: a signal generated near an exchange may traverse the public internet to a distant VPS---often incurring 80--120\,ms of transit alone---before an order is signed and returned to the exchange API, yielding total latencies of 180--320\,ms in typical retail configurations. In a low-latency trading context, the term \emph{low latency} denotes retail-grade webhook-to-ack times in the tens of milliseconds, distinct from the sub-10\,ms regime of exchange co-location~\cite{arnold2010latency,budish2015hft}.

Cloudflare Workers provide a fundamentally different execution model. User code runs in V8 isolates~\cite{jonas2019berkeley} distributed across more than 300 points of presence (PoPs). When combined with Service Bindings, Durable Objects, Queues, Smart Placement, and other edge primitives~\cite{cloudflare-workers,cloudflare-service-bindings,cloudflare-durable-objects,cloudflare-queues}, complete trading stacks can be constructed without operating any servers. Unlike conventional function-as-a-service (FaaS) platforms, Workers avoid container cold starts on the order of seconds~\cite{wang2018peeking,lloyd2018serverless}, and Service Bindings eliminate per-hop TLS and DNS overhead between microservices.

\textsc{HOOX} is a production-grade, fully open-source implementation of such a stack~\cite{hoox-project}. It ingests signals from TradingView webhooks, email, and Telegram; validates and routes them through a hardened gateway; executes trades across Binance, Bybit, and MEXC; manages risk autonomously; and provides observability, PDF compliance reporting, and DeFi execution. All components run as Cloudflare Workers and communicate internally without traversing the public internet.

\subsection{Contributions}

This paper describes the architecture, mechanisms, and operational results of building and running \textsc{HOOX}. The contributions are as follows:
\begin{enumerate}
  \item A detailed microservices architecture for edge-based trading using ten cooperating Workers, with a formal seven-stage signal lifecycle and five-layer security model.
  \item Design and implementation of \emph{duplicate-suppression} semantics using a Durable Object mutex at the gateway, with explicit discussion of fail-open behavior, queue at-least-once delivery, and idempotency key granularity.
  \item A reproducible evaluation toolchain---\texttt{hoox perf fastpath}, k6 load tests, and nightly CI artifacts---with a clear separation between internal probe latency and production exchange-ack latency (Figure~\ref{fig:latency-taxonomy}), including a fine-grained per-hop decomposition of the internal mesh.
  \item Operational measurements over a 12-month production deployment (July 2025--July 2026, N\,=\,18{,}742 production signals) demonstrating a median production signal-to-ack of 22\,ms on the direct path and 5.6--40$\times$ geographic RTT improvements versus a Virginia VPS baseline for exchange API reachability. Sample size and reconciliation methodology are reported.
  \item A practical demonstration that a complete trading infrastructure can operate within Cloudflare's free tier for typical retail volumes (${<}100{,}000$ requests/day).
\end{enumerate}

An extended technical reference---60 manifest-pinned code listings with a categorized index, runtime-semantics and advanced-mechanism deep dives, per-Worker implementation reference, ADRs, and a published test methodology with failure taxonomy---is available alongside this document in the open-source repository.

A focused companion paper, ``HOOX: A Proof-of-Concept Edge-Native Algorithmic Trading Platform on Cloudflare Workers'', is provided as both Markdown and LaTeX/PDF under \texttt{papers/hoox-proof-of-concept.*}. It is intended as a concise, citable summary of the PoC goals, primary results, and reproducibility claims.
