\section{Related Work}
\label{sec:related}

\paragraph{Open-source trading bots.} Frameworks such as Freqtrade and Jesse~\cite{freqtrade,jesse} assume a long-running process on a VPS or dedicated server. They offer rich strategy DSLs but inherit the latency and operational liabilities of centralized deployment.

\paragraph{Serverless trading.} AWS Lambda and Google Cloud Functions have been applied to trading automation~\cite{baldini2017serverless}, but typical architectures still route microservice traffic over public HTTP within a single region, without edge-wide Smart Placement or strongly consistent edge mutexes. The performance characteristics and cold-start penalties of general-purpose FaaS platforms have been characterized empirically~\cite{wang2018peeking,lloyd2018serverless,shahrad2020serverless} and inform the design choices in \textsc{HOOX}.

\paragraph{Low-latency trading and HFT.} Co-located high-frequency trading systems operate in the sub-10\,ms regime using kernel-bypass networking and exchange co-location~\cite{arnold2010latency,budish2015hft,hasbrouck2013lowlatency}. \textsc{HOOX} targets the retail-grade tens-of-milliseconds regime that lies between general FaaS deployments and co-located HFT, which has been studied empirically in the microstructure literature~\cite{hasbrouck2007empirical,hendershott2011does}.

\paragraph{On-chain automation.} DeFi keeper networks such as Chainlink Automation~\cite{chainlink-keepers} achieve low latency within a single blockchain domain but lack native multi-exchange CEX routing and rich off-chain signal sources.

\paragraph{Edge computing.} V8 isolate-based edge platforms~\cite{jonas2019berkeley,agache2020firecracker,cloudflare-workers} have been applied to content delivery, API gateways, and large-scale coordination tasks. CDN-style proximity routing has well-understood performance characteristics for general web traffic~\cite{nygren2010akamai,singh2015jupiter} and forms the substrate on which \textsc{HOOX} is built. \textsc{HOOX} extends the edge model to a latency-sensitive financial control plane with duplicate-suppression semantics, deterministic risk management, and the measurement taxonomy described in Section~\ref{sec:evaluation}.

\paragraph{Distributed coordination.} The duplicate-suppression mutex and queue-based resilience patterns used here are instances of broadly applicable distributed-systems techniques (atomic read-modify-write on strongly consistent storage, at-least-once delivery with idempotency keys) that have been studied for large-scale key-value stores~\cite{decandia2007dynamo,shahrad2020serverless,cloudflare-durable-objects}.

\textsc{HOOX} is distinguished by the exclusive composition of edge-native Service Bindings, Durable Object mutexes, Smart Placement, and integrated operational tooling into a retail-scale trading stack with a measured median 22\,ms production signal-to-ack on the direct path. This experience report shows how these primitives can be combined into a complete, maintainable, open-source retail trading system.
