\section{Reproducibility Protocol}
\label{app:repro}

Independent verifiers with a deployed \textsc{HOOX} stack and API credentials can reproduce the evaluation as follows (requires \texttt{@jango-blockchained/hoox-cli} \texttt{v0.9.3+} for the extended hop tracing). Sample sizes for the headline numbers reported in Section~\ref{sec:evaluation} are: N\,=\,200 synthetic fast-path probes (Table~\ref{tab:fastpath-detailed}), N\,=\,18{,}742 production signals over the 12-month window (Section~\ref{sec:reliability}), of which N\,=\,16{,}104 reached terminal exchange acknowledgment (Table~\ref{tab:production-latency}).

\paragraph{Fast-path probes (internal mesh, no exchange) --- extended hops.}
\begin{lstlisting}
hoox perf fastpath run --n 200 --concurrency 8
hoox perf fastpath report --from 1h
hoox trace events --last 1h --filter probe_id=...   # for full traces
\end{lstlisting}
Expect HTTP 200 with \texttt{status: "probed"}; the report includes the detailed multi-hop table. Confirm no new rows in the D1 \texttt{trades} table (integration test: \texttt{tests/integration/fastpath.test.ts}). Raw events are also queryable via the Observability API.

\paragraph{k6 load tests (gateway under concurrency).}
\begin{lstlisting}
BASE_URL=https://<gateway>.workers.dev \
HOOX_API_KEY=<key> \
k6 run tests/load/webhook-flow.js

HOOX_API_KEY=<key> \
k6 run tests/load/fastpath-audit.js
\end{lstlisting}
Default thresholds: webhook p95~$<$\,2000\,ms; fast-path audit p95~$<$\,3000\,ms.

\paragraph{Production exchange-ack latency.} Deploy with \texttt{queue\_disabled}, place micro-sized testnet orders without \texttt{probe: true}, and compare gateway \texttt{Date.now()} timestamps against exchange acknowledgment timestamps in Analytics Engine or D1 trade logs. To reproduce the 12-month production aggregates, a fresh deployment is required; raw production logs are intentionally not archived in the public repository.

\paragraph{Listing extraction.} All code excerpts are generated from the monorepo via \texttt{make listings} (see \texttt{papers/listings/manifest.yaml}). The categorized index is regenerated by \texttt{make listings-index} and is shipped in the extended monograph.

\paragraph{arXiv source bundle.} From the \texttt{papers/} directory, run \texttt{make arxiv-tarball} after \texttt{make pdf-tikz} to produce \texttt{dist/hoox-arxiv-submission.tar.gz} containing \LaTeX{} sources, figures, listings, and the compiled PDF. Submission metadata is in \texttt{arxiv-submission.md}.
